Graph Generators for Data Science: A Survey

### 2018-06-08 introduction.tex

In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}. Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}. In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern. Also, as in the other fields, quite often the respective real-world data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed). 
Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various order of magnitudes of the graph sizes thus leading to the inception of 
configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for 
algorithms and tools handling such data. 
%As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.

@@

To conclude the comparative study, we discuss open challenges and missing features of graph generators in view of identifying future challenges in data science.

\paragraph*{Contributions} The key contributions of this survey are as follows:
\begin{itemize}
  \item ...
\end{itemize}

...

@@

\paragraph*{Outline} The rest of the text is structured as follows: ...
% In Section~\ref{sec:preliminaries} we provide a brief introduction to graph theory and related terms.
% In Section~\ref{sec:classification} we classify the current Big graph Data applications.
% In Section~\ref{sec:generators} we introduce the existing graph data generators in the context of the proposed categories and their main features.
% Section~\ref{sec:comparison} provides comparison of the described generators.
% In Section~\ref{sec:challenges} we discuss challenges and open problems. And in Section~\ref{sec:conclusion} we conclude.

>>>>

In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}. Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}. In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern. Also, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various order of magnitudes of the graph sizes thus leading to the inception of
configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for
algorithms and tools handling such data.
%As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.

@@

To conclude the comparative study and provide a comprehensive view of the field,  we also discuss open challenges and missing features of graph generators in view of identifying future challenges in data science.

\paragraph*{Contributions} Our survey reviews the representatives of graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

\paragraph*{Outline} The rest of the text is structured as follows: 
In Section~\ref{sec:comparison} we provide the opening categorization and comparison of the generators. In Section~\ref{sec:generators} we overview the existing graph data generators and their main features in the frame of the proposed categories. In Section~\ref{sec:challenges} we discuss challenges and open problems of graph data synthesis and in Section~\ref{sec:conclusion} we conclude.
